Supplementary Information

### 2021-06-01 writing/appendix_a.Rmd
Draft appendix

---
title             : "Variation in Primary Care Prescribing in Wales due to COVID-19"
shorttitle        : "Welsh Primary Care COVID Prescribing"

author: 
  - name          : "Will Hardy"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Susan Murphy"
    affiliation   : "3"
  - name          : "Dyfrig Hughes"
    affiliation   : "1"
  - name          : "Daniel Hill-McManus"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Centre for Health Economics & Medicines Evaluation, Bangor University, LL55 2PZ"
  - id            : "2"
    institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"
  - id            : "3"
    institution   : "Betsi Cadwaladr University Health Board"

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "../references/library.bib"]

header-includes:
   - \usepackage{caption}
csl               : "../references/apa.csl"
always_allow_html : true
output            : 
  - html_document

---

@@

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = relevel(as_factor(drug), ref = "all_drugs"),
         sd = sd^.25)

gp_extract <- 
  map_dfr(.x = data_files,
          .f = ~(read_rds(.x) %>% 
            filter(practice_id %in% unique(differences$regional_unit))),
          .id = "drug") 
```

@@

# Introduction

# Methods

## Data

```{r, figure-1, fig.cap="Data processing flow."}
include_graphics("figures/data_flow.pdf")
```

```{r, table-2}
read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>%  
  filter(year == 2020) %>% 
  select(npat, ngp, dispensing, wimd2019:flu) %>% 
  mutate(across(p_male:flu, ~.x*100)) %>% 
  psych::describe() %>% 
  select(mean, sd, median, min, max) %>% 
  kable(digits = 2)
```

# Results

```{r, figure-2, fig.cap="Distribution of the difference between observed and forecast prescribing, expressed as a percentage of forecast prescribing. Grey line marks forecast level of prescribing. Pink shading covers duration of Wales' \"stay at home\" order. Please note the difference y-axis scales across the plots.", dpi=450}
differences_quantiles <- 
  differences %>% 
  na.omit() %>% 
  group_by(datename, drug) %>% 
  summarise(mean_prop = mean(prop, na.rm = T),
            med_prop = median(prop, na.rm = T),
            sd_prop = sd(prop, na.rm = T),
            se_prop = sd(prop, na.rm = T)/sqrt(length(prop)),
            enframe(quantile(prop, seq(.1,.9,.2)), 
                    "Percentile", "prop"),
            .groups = "drop") %>% 
  mutate(datename = month(datename),
         prop = 100*(prop - 1)) # Percentage change instead of proportion

differences_quantiles %>%
  mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  mutate(drug = case_when(drug == "all_drugs" ~ "All",
                          drug == "ace" ~ "ACE inhibitors",
                          drug == "adreno" ~ "Adrenoceptor agonists",
                          drug == "azithro" ~ "Azithromycin",
                          drug == "contra" ~ "Oral contraceptives",
                          drug == "cortico" ~ "Corticosteroids",
                          drug == "hcq" ~ "Hydroxycholoroquine",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "paracet" ~ "Paracetamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin"),
         drug = relevel(as_factor(drug), ref = "All")) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = Percentile)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(legend.position = "bottom", text = element_text(size = 10)) +
  scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
                        values = c(3,2,1,2,3), # Replicate line type
                        labels = c("10% lower; 90% upper", # Amalgamate line type labels
                                   "30% lower; 70% uppper", "50%")) +
  xlab("Month") +
  ylab("Percentage difference from forecast prescribing")

  ggsave(filename = "Draft 2/Figures/Figure 2.png", device = "png",
         width = 10.5)

```{r}
avg <- function(samples){
  if (length(samples) >= 1){
    return(sum(samples) / length(samples))
  }
  else{return(NaN)}
}

sample_SD <- function(samples){
  # Input is an vector of samples; result is the standard deviation
  mean = avg(samples)
  sum_of_squared_deviations <-  0
  sd <-  0
  if(length(samples) >= 2){
    for (datum in samples){
      sum_of_squared_deviations <- 
        sum_of_squared_deviations + ((datum - mean) * (datum - mean))
      sd = sqrt(sum_of_squared_deviations / (length(samples)-1))
    }
      return(sd)
  }
}

set.seed(134)
vec <- c(rnorm(n = 100), rnorm(n = 100))
vec_sd <- sd(vec)
sample_SD(vec)
compositeSD()

vec
compositeSD <- function(means, SDs, ncounts){
  #Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
  # See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
  #    Inputs are:
  #      means, the array of group means
  #      SDs, the array of group standard deviations
  #      ncounts, number of samples in each group (can be scalar
  #               if all groups have same number of samples)
  #    Result is the overall standard deviation.
  G <- length(means) # number of groups
  if(G != length(SDs)) stop("Inconsistent lengths (means & sds")
  if(!is.numeric(ncounts)) {(as.numeric(ncounts))}
  if(G != length(ncounts)) stop("Inconsistent lengths (means & ncounts)")

  # Calculate total number of samples, N, and grand mean, GM
  N = sum(ncounts)  # total number of samples
  if (N <= 1) stop(paste("Warning: only ", N, " samples, SD is incalculable"))
  GM <-  0.0
  for (i in 1:G){
    GM <- GM + means[i] * ncounts[i]
  }
  GM <- GM / N  # grand mean

  # calculate Error Sum of Squares
  ESS <-  0.0
  for (i in 1:G){
    ESS <- ESS + ((SDs[i])**2) * (ncounts[i] - 1)
  }

  # calculate Total Group Sum of Squares
  TGSS <-  0.0
  for (i in 1:G){
    TGSS <- TGSS + ((means[i]-GM)**2) * ncounts[i]
  }

  # calculate standard deviation as square root of grand variance
  result <- sqrt((ESS+TGSS)/(N-1))
  return(result)
}

samples = 0:9
print(paste("avg =", avg(samples)))
sd = sample_SD(samples)
print(paste("sd =", sd))
pt1 = c(0,1,2)
pt2 = c(3,4)
pt3 = c(5,6,7,8,9)
means <- c(avg(pt1), avg(pt2), avg(pt3))
SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
ncounts <- c(length(pt1), length(pt2), length(pt3))
sd2 <- compositeSD(means, SDs, ncounts)
print(paste("sd2 =", sd2))

samples = 0:8
print(paste("avg =", avg(samples)))
sd = sample_SD(samples)
print(paste("sd =", sd))
pt1 = c(0,1,2)
pt2 = c(3,4,5)
pt3 = c(6,7,8)
means <- c(avg(pt1), avg(pt2), avg(pt3))
SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
ncounts <- c(length(pt1), length(pt2), length(pt3))
sd2 <- compositeSD(means, SDs, ncounts)
print(paste("sd2 =", sd2))

```{python}

from __future__ import print_function, division  # requires python 2.6 or later (2.7 or later preferred)
import math

__all__ = ['iterable', 'avg', 'sample_SD', 'composite_SD']

def iterable(obj):
    '''True iff obj is iterable: a list, tuple, or string.'''
    return hasattr(obj, '__contains__')

def avg(samples):
    if len(samples) >= 1:
        return sum(samples) / len(samples)
    return float('nan')

def sample_SD(samples):
    '''input is an array of samples; result is the standard deviation'''
    mean = avg(samples)
    sum_of_squared_deviations = 0;
    sd = 0
    if len(samples) >= 2:
        for datum in samples:
            sum_of_squared_deviations += ((datum - mean) * (datum - mean));
        sd = math.sqrt(sum_of_squared_deviations / (len(samples)-1) );
    return sd

def composite_SD(means, SDs, ncounts):
    '''Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
       See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
       Inputs are:
         means, the array of group means
         SDs, the array of group standard deviations
         ncounts, number of samples in each group (can be scalar
                  if all groups have same number of samples)
       Result is the overall standard deviation.
    '''
    G = len(means)  # number of groups
    if G != len(SDs):
        raise Exception('inconsistent list lengths')
    if not iterable(ncounts):
        ncounts = [ncounts] * G  # convert scalar ncounts to array
    elif G != len(ncounts):
        raise Exception('wrong ncounts list length')

    # calculate total number of samples, N, and grand mean, GM
    N = sum(ncounts)  # total number of samples
    if N <= 1:
        raise Exception("Warning: only " + str(N) + " samples, SD is incalculable")
    GM = 0.0
    for i in range(G):
        GM += means[i] * ncounts[i]
    GM /= N  # grand mean

    # calculate Error Sum of Squares
    ESS = 0.0
    for i in range(G):
        ESS += ((SDs[i])**2) * (ncounts[i] - 1)

    # calculate Total Group Sum of Squares
    TGSS = 0.0
    for i in range(G):
        TGSS += ((means[i]-GM)**2) * ncounts[i]

    # calculate standard deviation as square root of grand variance
    result = math.sqrt((ESS+TGSS)/(N-1))
    return result

samples = range(10)
print(samples)
print('avg=', avg(samples))
sd = sample_SD(samples)
print('sd=', sd)
pt1 = [0,1,2]
pt2 = [3,4]
pt3 = [5,6,7,8,9]
means = [avg(pt1), avg(pt2), avg(pt3)]
SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
ncounts = [len(pt1), len(pt2), len(pt3)]
sd2 = composite_SD(means, SDs, ncounts)
print('sd2=', sd2)

samples = range(9)
print('avg=', avg(samples))
sd = sample_SD(samples)
print('sd=', sd)
pt1 = [0,1,2]
pt2 = [3,4,5]
pt3 = [6,7,8]
means = [avg(pt1), avg(pt2), avg(pt3)]
SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
ncounts = 3
sd2 = composite_SD(means, SDs, ncounts)
print('sd2=', sd2)
```

```{r, table-3-single-fcts}
nat_data <- 
  data_files %>% 
  map_dfr(read_rds, .id = "drug") %>% 
  group_by(drug, datename) %>% 
  summarise(n = sum(quantity), .groups = "drop")

plan(multisession)
precribing_cv_models <- 
  nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  serCymruTools::regionalCV(cv_dist = 8, init = 36, step = 3)
plan(sequential)

precribing_cv_models

best_model <- 
  precribing_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model %>% 
  filter(MAPE > 50)

plan(cluster)
system.time(prescribing_fcsts <-
                nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  as_tsibble(index = "datename", key = "regional_unit") %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts())  
plan(sequential)

best_model_discrep <- 
  best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(prescribing_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(                nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) , 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - med, # observed - forecast
         prop = n / med) %>% 
  ungroup()

best_model_discrep %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(1,nrow(.))),
            .mean = sum(.mean)
  )

best_model_discrep %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  group_by(regional_unit) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(1,5)),
            .mean = sum(.mean),
            ) %>% 
  mutate(lb = .mean - 1.96*sd,
         ub = .mean + 1.96*sd,
         lb_mean_pct_change = (100 * (n - ub)/ ub),
         mean_pct_change = (100 * (n - .mean)/ .mean),
         ub_mean_pct_change = (100 * (n - lb)/ lb),
         ) %>% 
  select(regional_unit, lb_mean_pct_change, mean_pct_change, ub_mean_pct_change)
  ggplot(aes(x = regional_unit, y = mean_pct_change)) +
  geom_col() +
  geom_errorbar(aes(ymin = lb_mean_pct_change, ymax = ub_mean_pct_change))
```

```{r, table-3}
# https://stats.stackexchange.com/questions/454120/how-can-i-calculate-uncertainty-of-the-mean-of-a-set-of-samples-with-different-u

#
# An iterative procedure to estimate mean and variance from a set of 
# measurements `x` made with known measurement errors `sigma.i`.
#
var.wt <- function(x, sigma.i, thresh=1e-6, iter.max=1e4) { # Changed from values in example (1e-6, 200)
  #
  # To avoid giving undue weight to any subset, all SDs should be nonzero.
  #
  if (missing(sigma.i)) sigma.i <- rep(0, length(x)) # No measurement error
  tol <- sum(abs(x)) * 1e-16
  sigma.i[sigma.i <= 0] <- min(c(tol, sigma.i[sigma.i > 0])) / 2
  #
  # Initialize.
  #
  v <- var(x)
  n <- length(x)
  S <- mean(sigma.i^2) # Avoids recomputing this constant within the loop
  for (i in 1:iter.max) {
    w <- 1/(v + sigma.i^2); w <- w / sum(w)
    m <- sum(x * w)
    v.0 <- max(0, sum((x-m)^2 * w) * n / (n-1) - S) 
    if (v <= v.0 * (1+thresh) && v.0 <= v * (1+thresh)) break
    v <- v.0
  }
  if (i >= iter.max) warning("Maximum iteration count exceeded.")
  list(Variance=v, Mean=m, Iterations=i)
}

sample_bound <- function(mean = ".mean", variance = "sd", 
                         bound = c(.975, .5, .025), data = .){

  # The data in the question.
  #
  x <- data[[mean]]
  sigma.i <- data[[variance]]
  (s <- var.wt(x, sigma.i))
  #
  # A parametric bootstrap.
  #
  n <- length(x)
  sigma <- sqrt(s$Variance)
  mu <- s$Mean
  set.seed(17)
  X <- replicate(5e3, {
    y <- rnorm(n, mu, sigma)
    epsilon <- rnorm(n, 0, sigma.i)
    x <- y + epsilon
    var.wt(x, sigma.i)
  })
  X <- matrix(unlist(X), 3)

  return(quantile(X[2,], bound))
}

monthly_diffs <- 
  differences %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug, datename) %>% 
  group_modify(~ {
    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
      tibble::enframe(name = "bound", value = "value")
  }) %>% 
  left_join(differences %>% 
              select(drug, datename, .mean, sd, n) %>% 
              na.omit() %>% 
              group_by(drug, datename) %>% 
              summarise(n = mean(n, na.rm = TRUE),
                        .mean = mean(.mean, na.rm = TRUE),
                        .group = "drop"), 
            by = c("drug", "datename")) %>% 
  mutate(p_change = 100*n / value) %>% # Difference as a proportion
  pivot_wider(id_cols = c("drug", "datename", "n", ".mean"), 
              names_from = "bound", values_from ="value") %>% 
  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
  rename("LB" = `97.5%`,
         "Mean" = `50%`,
         "UB" = `2.5%`) %>% 
  mutate(datename = month(datename),
         pct_change = paste0(printnum(Mean), 
                             "[", printnum(LB), ",", printnum(UB), "]"))

lockdown_diff_bounds <- 
  differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  group_modify(~ {
    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
      tibble::enframe(name = "bound", value = "value")
  })

lockdown_diff_bounds_wide <- 
  lockdown_diff_bounds %>% 
  pivot_wider(id_cols = "drug", names_from = "bound", values_from = "value") %>% 
  rename("lb" = `97.5%`,
         "mean" = `50%`,
         "ub" = `2.5%`) # returns mean quantity forecast per month in lockdown

lockdown_diff_obs <- 
  differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  select(drug, datename, .mean, sd, n, med) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  summarise(n = mean(n, na.rm = FALSE),
            .mean = mean(.mean, na.rm = FALSE),
            med_med = median(med),
            mean_med = mean(med),
            .groups = "drop")

left_join(lockdown_diff_obs, lockdown_diff_bounds_wide) %>% 
  mutate(across(.mean:ub, ~(n-.x)/.x))

###
lockdown_diffs <- 
  differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  group_modify(~ {
    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
      tibble::enframe(name = "bound", value = "value")
  }) %>% 
  left_join(differences %>% 
              filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
              select(drug, datename, .mean, sd, n) %>% 
              na.omit() %>% 
              group_by(drug) %>% 
              summarise(n = mean(n, na.rm = TRUE),
                        .mean = mean(.mean, na.rm = TRUE),
                        .groups = "drop"), 
            by = c("drug")) %>% 
  mutate(p_change = 100 * n / value) %>% # Difference as a proportion
  pivot_wider(id_cols = c("drug", "n", ".mean"), 
              names_from = "bound", values_from ="value") %>% 
  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
  rename("LB" = `97.5%`,
         "Mean" = `50%`,
         "UB" = `2.5%`) %>% 
    mutate(lockdown = paste0(printnum(Mean), 
                             "[", printnum(LB), ",", printnum(UB), "]"))

lockdown_diffs %>% 
  select(drug, lockdown) %>% 
  left_join(monthly_diffs %>% 
              pivot_wider(id_cols = "drug", names_from = "datename", 
                          values_from = "pct_change"), by = "drug") %>% 
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>% 
  add_header_above(header = c(" " = 1, 
                              "Mean percentage change [95% CI]" = 9)) %>% 
  landscape()
```

```{r}
differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  group_by(drug) %>% 
  summarise(n = sum(n),
            .mean = sum(.mean)) %>% 
  mutate(pct_change = 100 * (n - .mean ) / .mean)
```

```{r, eval=FALSE}
differences %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  summarise(across(where(is.numeric),.fns = max))
```

```{r}
gp_extract %>% 
  filter(str_detect(datename, "-19")) %>% 
  group_by(drug) %>% 
  summarise(n = sum(quantity)/1e6) %>% 
  left_join(lockdown_diffs %>% 
  select(drug, lockdown), by = "drug")
```

```{r, mean-change-plot}
monthly_diffs %>% 
  ggplot(aes(x = datename, group = drug)) +
  geom_line(aes(y = Mean)) +
  geom_ribbon(aes(ymin = LB, ymax = UB, fill = drug), alpha = .4) +
  facet_wrap(~drug, scales = "free")

```{r}
differences %>% 
  group_by(drug) %>% 
  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
            n = sum(n, na.rm = TRUE),
            pct = 100*discrepancy / n)

differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  group_by(drug) %>% 
  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
            n = sum(n, na.rm = TRUE),
            pct = 100*discrepancy / n) %>% 
  ggplot(aes(x = reorder(drug, pct), y = pct)) +
  geom_col()
```

# Discussion

# References

<div custom-style='Title'>Appendix </div>

@@

# Forecasting

@@

```{r, all-prescribing-model-accuracy-hist1, fig.cap="All prescribing, model accuracy", eval=FALSE}
p1 <- all_prescribing_fable_fits %>% 
  na.omit() %>% 
  ggplot(aes(x = reorder(.model, RMSE, sort), y = RMSE)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90))

@@

# Forecasting

```{r, all-prescribing-cv-plot1, fig.cap="All prescribing, best model CV fit", eval=FALSE}
all_prescribing_best_cv_model <- 
  augment(all_prescribing_fable_models) %>% 
  as_tibble() %>% 
  filter(.model == all_prescribing_best_model$.model)

```{r, all-prescribing-forecast-plot1, warning=FALSE, fig.cap="All prescribing, best model fit and forecast.", eval=FALSE}
plan(cluster)
all_prescribing %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
            data = all_prescribing_covid_forecast) +
  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
                  fill = "Forecast"), alpha = .2,
              data = all_prescribing_covid_forecast) +
  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, 
                  fill = "Forecast"), alpha = .3,
              data = all_prescribing_covid_forecast) +
  # geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
  #           data = fableModels(all_prescribing_pre_cv19) %>% 
  #             augment() %>% 
  #             as_tibble() %>% 
  #             filter(.model == all_prescribing_best_model$.model) %>% 
  #             group_by(datename) %>% 
  #             summarise(fitted = median(.fitted, na.rm = TRUE))) +
  geom_vline(xintercept = ymd("2020-03-01"), lty = 3) +
  coord_cartesian(xlim = c(dmy("01-11-2018"), dmy("01-08-2020"))) +
  scale_x_yearmonth(breaks = "6 months", minor_breaks = "1 months")+
  xlab("Date") +
  ylab("Mean daily prescribing volume")

```{r, all-prescribing-pct-change-plot1, fig.cap="Percentage difference in all prescribing.", eval=FALSE}
all_prescribing %>% 
  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
  ggplot(aes(x = datename, y = (100*n/med)-100)) +
  geom_line() +
  geom_hline(yintercept = 0, lty = 3)
```

```{r, excluded-practices-tab1}
months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
            "2020 Jul","2020 Aug")

@@

```{r best-cv-model-type, fig.cap="Performance by model type."}
cv_model_files %>% 
  map_dfr(.id = "drug", .f = read_rds) %>% 
  rankModels() %>% 
  group_by(drug, regional_unit) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50) %>% 
  ggplot(aes(x = as.factor(.model))) +
  geom_bar() +
  xlab("Model") +
  theme(axis.text.x = element_text(angle = 90))
```

@@

```{r, oac-gen-trend, eval = FALSE}
oac <- read_rds(data_files[9])

>>>>

---
title: Supplementary Information
short_title: COVID-19 Prescribing
bibliography      : ["r-references.bib", "../references/library.bib"]
ouput: html_document
---

@@

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = relevel(as_factor(drug), ref = "all_drugs"))

@@

@@

## Reproducability and code

We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.

## Forecasting

@@

@@

@@

```{r best-cv-model-type, fig.cap="Performance by model type."}
cv_model_files %>% 
  map_dfr(.id = "drug", .f = read_rds) %>% 
  rankModels() %>% 
  group_by(drug, regional_unit) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50) %>% 
  ggplot(aes(x = as.factor(.model))) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90))
```

@@

```{r, oac-gen-trend, eval=FALSE}
oac <- read_rds(data_files[9])
